---
title: "Lab 6"
author: "Karisa Ke"
format: html
embed-resources: true
editor: visual
---

```{r}
library(readr)
library(dplyr)
mt_samples <- read_csv("https://raw.githubusercontent.com/USCbiostats/data-science-data/master/00_mtsamples/mtsamples.csv")
mt_samples <- mt_samples %>%
  select(description, medical_specialty, transcription)

head(mt_samples)
```

## Question 1

```{r}
mt_samples %>%
  count(medical_specialty, sort = TRUE)
```

Looks like these medical specialties are not related to each other, with surgery has the most count.

## Question 2

```{r}
library(tidytext)

mt_samples %>%
  unnest_tokens(word, transcription)
```

```{r}
mt_samples %>%
  unnest_tokens(word, transcription) %>%
  count(word, sort = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
library(forcats)

mt_samples %>%
  unnest_tokens(word, transcription) %>%
  count(word, sort = TRUE) %>%
  top_n(20, n) %>%
  ggplot(aes(x = n, y = fct_reorder(word, n))) +
  geom_col() +
  labs(title = "Top 20 Most Frequent Words", x = "Frequency", y = "Word")
```

The top 20 most frequent words don't make any sense, they are very common words in English and we are not able to extract useful information about the original text.

## Question 3

```{r}
library(stopwords)
library(stringr)
mt_samples %>%
  unnest_tokens(word, transcription) %>%
  anti_join(stop_words) %>%
  filter(!str_detect(word, "^\\d+$")) %>%
  count(word, sort = TRUE) %>%
  top_n(20, n) %>%
  ggplot(aes(x = n, y = reorder(word, n))) +
  geom_col() +
  labs(title = "Top 20 Most Frequent Words (Stopwords and Numbers Removed)", x = "Frequency", y = "Word")
```

After removing stop words, we have a better idea about what the text is about, it's clearly related to medicals.

## Question 4

```{r}
mt_samples %>%
  unnest_ngrams(ngram, transcription, n = 2) %>%
  count(ngram, sort = TRUE)
```

```{r}
mt_samples %>%
  unnest_ngrams(ngram, transcription, n = 3) %>%
  count(ngram, sort = TRUE)
```

The bi-grams and tri-grams don't really make any differences.

## Question 5

```{r}
chosen_word <- "the patient"

mt_samples %>%
  unnest_tokens(word, transcription) %>%
  filter(word == chosen_word) %>%
  select(-description) %>%
  group_by(medical_specialty) %>%
  arrange(word) %>%
  summarise(
    words_before = lag(word),
    chosen_word = word,
    words_after = lead(word)
  )
```

## Question 6

```{r}
mt_samples %>%
  unnest_tokens(word, transcription) %>%
  anti_join(stop_words) %>%
  filter(!str_detect(word, "^\\d+$")) %>%
  group_by(medical_specialty) %>%
  count(word, sort = TRUE) %>%
  top_n(1, n)
```

```{r}
mt_samples %>%
  unnest_tokens(word, transcription) %>%
  anti_join(stop_words) %>%
  filter(!str_detect(word, "^\\d+$")) %>%
  group_by(medical_specialty) %>%
  count(word, sort = TRUE) %>%
  top_n(5, n)
```
